---
title: '2.15'
author: "The Indoor Kites (Saad Khan, Xiao Zang, Nate Sandholtz, Jacob
Mortensen)"
date: "10/4/2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Proof of Probability Integral Transform
Let $X$ be a random variable with continuous, strictly increasing CDF $F$ and let $Y = F_X(X)$ so that $X = F^{-1}_X(Y)$.

\begin{align*}
F_Y(y) &= P(Y \le y) \\
&= P(F_X(X) \le y) \\
&= P(X \le F^{-1}_X(y)) \\
&= \int_{-\infty}^{F^{-1}_X(y)} f(x)dx \\
&= F_X(x)\bigg|_{-\infty}^{F^{-1}_X(y)} \\
&= F_X(F^{-1}_X(y)) - F_X(-\infty) \\
&= y - 0
\end{align*}

Since $F_Y(y)=y$, $\frac{d}{dy} F_Y(y) = f_Y(y) = 1$, the density of a standard uniform distribution. 

Now let $U \sim Unif(0,1)$ and let $X = F^{-1}(U)$. Then 
\begin{align*}
F_X(x) &= P(X \le x) \\
&= P(F^{-1}(U) \le x) \\
&= P(U \le F(x)) \\
&= \int_{0}^{F(x)} 1du \\
&= u \bigg|_0^{F(x)} \\
&= F(x) - 0\\ 
&= F(x)
\end{align*}
and so we conclude that $X \sim F$. 

A program that converts standard uniform random variables into draws from an Exponential $\beta$ distribution is shown below.

```{r, gen-rvs-function}
gen_exp <- function(u, beta) {
  # The quantile function (qexp) is the inverse CDF
  # We use 1/beta because R uses the rate parameterization for the exponential
  # while the book uses the scale parameterization.
  qexp(u, 1/beta)
}

# Generate 1000 standard uniform draws and convert them
u <- runif(1000)
beta <- 4
exp_draws <- gen_exp(u, beta)

# Draw 1000 random draws from the built-in R function for comparison
rexp_draws <- rexp(1000, 1/beta)

ggplot(data.frame(exp = exp_draws, rexp = rexp_draws)) +
  geom_density(aes(x = exp, colour = "Our Func."), alpha = 0.5) +
  geom_density(aes(x = rexp, colour = "Built In Func."), alpha = 0.5) + 
  stat_function(aes(x = x, colour = "True Density"), 
                data = data.frame(x = -1:30), 
                fun = dexp, args = list(rate = 1/beta)) +
  ggtitle(bquote("Random Draws from Exponential("~beta~")")) +
  xlab("X") +
  ylab("Density") +
  scale_colour_manual(name = "Guide", values = c("Our Func." = "royalblue2",
                    "Built In Func." = "firebrick",
                    "True Density" = "darkgreen")) 
