---
  output: pdf_document
---
# S830 assignment 2 (group portion)
## Grace G. Hsu, Ran Wang

## CH2 Q15

```{r}
# @param unif uniform(0, 1) random variables; i.e. vector of samples from the
#   unif(0, 1) distribution
# @param b scale parameter for exponential distribution (b = 1/rate); default is
#   1
#   
# @return values from a exponential distribution with scale = b = 1/rate; i.e.
#   the Exp(b) random variables
Exp.generator <- function(unif, b = 1) {
  qexp(p = unif, rate = 1/b)
}

## testing the generator
set.seed(830)
unif.rvs <- runif(n = 1000)
test <- Exp.generator(unif = unif.rvs)

histtest <- hist(test)
plot(x = histtest$mids, y = histtest$density, pch = 16)
points(x = histtest$mids, y = dexp(x = histtest$mids), cex = 0.2, col = "green")  
# very close to histogram points
```

## CH3 Q11

```{r}
## simulate 
n <- 10000
num.runs <- 4

set.seed(830)
runs <- matrix(NA, nrow = n, ncol = num.runs)
for (j in 1:num.runs) {
  Yi <- sample(x = c(-1, 1), size = 10000, replace = TRUE)
  Xi <- cumsum(Yi)
  runs[,j] <- Xi
}

## plot all simulations
cols = c("black", "red", "blue", "green", "brown", "purple", "yellow", "pink")
for (j in 1:num.runs) {
  if (j == 1) {
    plot(x = 1:n, y = runs[,j], pch = 16, cex = 0.5,
         ylim = c(-105, 105),
         main = "4 Random walk simulations; p = 1/2",
         xlab = "n", ylab = "Xn")
    abline(h = 0)
    abline(h = sqrt(n))
    abline(h = -sqrt(n))
  } else {
    points(x = 1:n, y = runs[,j], col = cols[j], pch = 16, cex = 0.5)
  }
}
```

* Note that we really just simulated 4 random walks (see CH3 Q4).

* Even though the expectation of Xn is 0, the variance is n = `r n` and hence
the standard deviation is `r sqrt(n)`.

* Thus, as n increases, we expect each run to deviate more from each other as
the variance increases; this is sort of reflected in the plot. Note that all
four still cross zero back and forth as expected.

